
To find out whether sharing the clause database was beneficial to the
same-chip portfolio-approach solver, we ran AzuDICI in three different
versions (sharing all the clauses, sharing none of the clauses and
sharing only binaru clauses) on eight representative problems
(XXXNAMESXXX) using one to six threads. Each run was repeated five
times to clean up potential system noise. XXXKeiraXXX

\subsection{Same search experiments}
\label{sec:samesearch}

For this experiment, AzuDICI was modified to carry out the {\em same}
search in each thread (i.e., there is no lemma sharing among
threads). For each AzuDICI version, we measured the time needed to
solve each benchmark, and the percentage of LLC misses. The results
for this are shown in Table \ref{tbl:table} below.

[[[[TABLE WITH RESULTS]]]]

[[[[GRAPH AGGREGATING EXEC TIME PER THREAD]]]]

[[[[GRAPH PERCENNTAGE LLC MISSES PER THREAD]]]]

[[[[ANALYSIS]]]]

As is evident, our implementation shows that physically sharing the
clause database is beneficial to avoid cache contention.

\subsection{Different search experiments}
\label{sec:diffsearch}

Our previous experiment validates our implementation of the
solver. Nonetheless, the results are not generalizable to a
full-featured SAT solver. It may be the case that while threads are
carrying out the same search, it is more likely that they will access
the same data. Whereas different search threads are clearly not
necessarily accessing the same data at the same time.

To find out how a real portfolio-approach SAT solver implementing
different levels of physical clause sharing behave, we ran AzuDICI in
the same three different versions as before (sharing-all, share-none
and share-bin) on eight different (harder) problems (XXXNAMESXXX)
using one to six threads and with a 5-minute timout. Each run was
repeated five times to clean up potential system noise. XXXKeiraXXX

[[[[TABLE WITH RESULTS]]]]

[[[[GRAPH PERCENNTAGE LLC MISSES PER THREAD]]]]

[[[[ANALYSIS]]]]

From these data, we may conclude that physically sharing the whole
clause database does not improve the cache performance of the
portfolio-approach-based SAT solvers

% Shared-all performs well wrt to cache misses, but that is not
% necessarily true for time. In general, the number of cache loads is
% larger when we are sharing the clause DB. Still, we think this is an
% implementation issue. That is, even if we may be saving on cache
% misses while sharing data, the more complex nature of the
% implementation can negatively influence overall time.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "sat"
%%% End: 
